### 2016-05-20 paper/mathematical_formulation.tex
Small additions.

\chapter{Mathematical Formulation} \label{chap:form}

In Section \ref{sec:setup}, we define the goal-oriented inverse problem. In Section \ref{sec:deriv}, we derive an a posteriori estimate for the error in the QoI, as compared to that which would have resulted from solving the inverse problem with a high-fidelity model. In Section \ref{sec:limits}, we discuss the limitations of the error estimate.

@@

Consider a model for which the Galerkin formulation of the weak form is written as
\begin{equation}
a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\label{eq:weakForm}
\end{equation}
where $u\in U$ is the state, $q\in Q$ are the unknown parameters, $\phi$ is a test function, and $U,Q$ are Hilbert spaces. The form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.

We define an observation operator $C:U\to\R^{n_d}$ that maps the state to $n_d$ predicted observations; we denote the actual observations by $d\in\R^{n_d}$. The unknown parameters can then be inferred by minimizing the difference between the predicted and actual observations. This inverse problem is often ill-posed; the observations are noisy and sparse and thus insufficiently informative to uniquely determine the parameters. To remedy this, regularization is used to inject prior information or beliefs about the parameters. The inverse problem with regularization can be written as a constrained optimization problem
\begin{equation}
\begin{array}{r@{}c}
\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \\ \textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\end{array}
\label{eq:invOpt}
\end{equation}
where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization penalty term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model in Equation (\ref{eq:weakForm}).

@@

A given physical system need not have a unique model that can describe it; there may be various models of different fidelities. For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.

>>>>

\section{Mathematical Formulation}\label{sect:form}
%
We first introduce the high fidelity goal oriented inverse problem formally, providing definitions and variational statments. Then we will derive a rigorous, a posteriori error estimate for the error induced in the QoI due to the use of mixed/lower fidelity constraints.

@@

We seek to infer a parameter $q \in Q$, where $Q$ is a Hilbert space. Consider a state variable $u \in U$, which satisfies a bilinear form $a:U \times U \to \Reals$, such that,
\begin{equation}
a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\label{eq:weakForm}
\end{equation}
where the form $a$ and functional $\ell$ are linear with respect to the arguments in the second pair of parentheses.

We define an observation operator $C:U\to\Reals^{n_d}$ that maps the state to $n_d$ predicted observations; we denote the actual observations by $d\in\R^{n_d}$. The unknown parameters can then be inferred by minimizing the difference between the predicted and actual observations. This inverse problem is often ill-posed; the observations are noisy and sparse and thus insufficiently informative to uniquely determine the parameters. To remedy this, regularization is used to inject prior information or beliefs about the parameters. The inverse problem with regularization can be written as a constrained optimization problem
\begin{equation}
\begin{array}{r@{}c}
\min\limits_{q,u} & \quad J(q,u)=\frac{1}{2}\|d-C(u)\|_2^2 + R(q) \\ \textrm{s.t. }& \quad a(u,q)(\phi)=\ell(q)(\phi),\quad\forall\phi\in U,
\end{array}
\label{eq:invOpt}
\end{equation}
where we aim to minimize the cost function $J$, which includes the mismatch between predicted and actual observations and a regularization penalty term $R(q)$, subject to the state $u$ and parameters $q$ satisfying the model in Equation (\ref{eq:weakForm}).

@@

A given physical system need not have a unique model that can describe it; there may be various models of different fidelities. For a given hierarchy of models, consider the QoI calculated from inferring the parameters with the highest-fidelity model; we take this QoI to be the value with which we compare other QoI estimates. In this section we derive an a posteriori estimate for the error in the QoI from inferring the parameters with a lower-fidelity model, as compared to that which would have resulted from solving the inverse problem with the highest-fidelity model.
%
\begin{theorem}
\label{thm:error_estimate}
\begin{multline}
I(q_{HF},u_{HF})-I(q_{LF},u_{LF})=\\-\frac{1}{2}\mathcal{M}'_{HF,\Psi}(\Psi_{LF})(\Lambda)+\mathcal M_{HF}(\Psi_{LF})-\mathcal M_{LF}(\Psi_{LF})+\mathcal{R}(e^3).
\label{eq:finErrExp}
\end{multline}
\end{theorem}
%
